#fig2 extended data fig 2 extended data fig 3
```{r}
library(dplyr)
library(stringr)
library(viridis)
library(Seurat)
library(patchwork)
library(sctransform)
library(ggplot2)
library(harmony)
library(ggsci)
library(ggpubr)
library(pheatmap)
library(Matrix)
library(RColorBrewer)
library(scales)
library(data.table)
library(stats)
library(tibble)
library(tidyr)
```

```{r}
setwd("C:/Users/fkady/Desktop/hif1a paper figures/scseq figure/aesthetic")

# WT
wt_dir <- 'C:/Users/fkady/Desktop/hif1a paper figures/scseq figure/aesthetic/MGI0074_1_HIF1a_ctrl/filtered_feature_bc_matrix'
wt.data <- Read10X(data.dir =wt_dir)
WT <- CreateSeuratObject(counts = wt.data, min.cells = 3, min.features = 200)
WT$condition <- "WT"

# KO
ko_dir <- 'C:/Users/fkady/Desktop/hif1a paper figures/scseq figure/aesthetic/MGI0074_1_HIF1a_KO/filtered_feature_bc_matrix'
ko.data <- Read10X(data.dir =ko_dir)
KO <- CreateSeuratObject(counts = ko.data, min.cells = 3, min.features = 200)
KO$condition <- "KO"

merged <- merge(WT, y = c(KO))
```
#QC
```{r}
merged[["propmt"]] <- PercentageFeatureSet(merged, pattern = "^mt-")
VlnPlot(merged, features = c("nFeature_RNA", "nCount_RNA", "propmt"), ncol = 3, pt.size=0)
```

```{r}
merged
```

```{r}

merged2 <- subset(merged, subset = nFeature_RNA > 500 & nFeature_RNA < 5000 & propmt < 10 & nCount_RNA < 20000)

```

```{r}
merged2
```

```{r}
png(filename="./qc violin plot.png", width=18, height=10, units="cm", res=300)
VlnPlot(merged2, features = c("nFeature_RNA", "nCount_RNA", "propmt"), group.by = "orig.ident", ncol = 3, pt.size=0)
dev.off()
```

#SCT transform and filter
```{r}
DefaultAssay(merged2) <- 'RNA'
merged2 <- SCTransform(merged2, vars.to.regress = c("propmt", "nCount_RNA"), verbose = TRUE)
```

```{r}
merged2 <- RunPCA(merged2, features = VariableFeatures(object = merged2), npcs=100, verbose=TRUE)
```

```{r}
ElbowPlot(merged2, ndims = 50)
```

```{r}
merged2 <- RunUMAP(merged2, reduction = "pca", dims = 1:40)
merged2 <- FindNeighbors(merged2, reduction = "pca", dims = 1:40)
merged2 <- FindClusters(merged2, graph.name = "SCT_snn", algorithm = 3, resolution = c(0.4), verbose = FALSE)
```

```{r}
DimPlot(merged2, reduction = "umap", label = TRUE)
```

```{r}
setwd("C:/Users/fkady/Desktop/andrew reclustered no ccrl2 121422")
DefaultAssay(merged2) <- 'SCT'
rna.markers <- FindAllMarkers(merged2, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.25)
write.csv(rna.markers, file ="./DGE_GEX_res0.4.csv", quote = FALSE)
```


#Remove Non Myeloid
```{r}
#5 t cells
#14 nk cells
#7 endothelial
#11 fibroblast
#15 b cells

merged3 <- subset(merged2, idents = c("0","1","2","3","4","6","8","9","10","12","13"))
```

```{r}
DefaultAssay(merged3) <- 'RNA'
merged3 <- SCTransform(merged3, vars.to.regress = c("propmt", "nCount_RNA"), verbose = TRUE)
merged3 <- RunPCA(merged3, features = VariableFeatures(object = merged3), npcs=100, verbose=TRUE)
```


```{r}
ElbowPlot(merged3, ndims = 50)
```

```{r}
merged3 <- RunUMAP(merged3, reduction = "pca", dims = 1:40)
merged3 <- FindNeighbors(merged3, reduction = "pca", dims = 1:40)
merged3 <- FindClusters(merged3, graph.name = "SCT_snn", algorithm = 3, resolution = c(0.4), verbose = FALSE)
```

```{r}
DimPlot(merged3, reduction = "umap", label = TRUE)
```

```{r}
DefaultAssay(merged3) <- 'SCT'
rna.markers <- FindAllMarkers(merged3, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.25)
write.csv(rna.markers, file ="./merged3_DGE_GEX_res0.4.csv", quote = FALSE)
```

# Remove non myeloid
```{r}

#3 neutrophils
#4 neutrophils
#5 mitochondrial genes
#6 neutrophils
#10 cardiomyocytes

merged4 <- subset(merged3, idents = c("0","1","2","7","8","9","11"))
```

```{r}
DefaultAssay(merged4) <- 'RNA'
merged4 <- SCTransform(merged4, vars.to.regress = c("propmt", "nCount_RNA"), verbose = TRUE)
merged4 <- RunPCA(merged4, features = VariableFeatures(object = merged4), npcs=100, verbose=TRUE)
```

```{r}
ElbowPlot(merged4, ndims = 50)
```

```{r}
merged4 <- RunUMAP(merged4, reduction = "pca", dims = 1:40)
merged4 <- FindNeighbors(merged4, reduction = "pca", dims = 1:40)
merged4 <- FindClusters(merged4, graph.name = "SCT_snn", algorithm = 3, resolution = c(0.4), verbose = FALSE)
```

```{r}
DimPlot(merged4, reduction = "umap", label = TRUE, group.by = "SCT_snn_res.0.4")
```

```{r}
DefaultAssay(merged4) <- 'SCT'
rna.markers <- FindAllMarkers(merged4, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.25)
write.csv(rna.markers, file ="./merged4_DGE_GEX_res0.4.csv", quote = FALSE)
```

# Remove non myeloid
```{r}
#8 neutrophils

merged5 <- subset(merged4, idents = c("0","1","2","3","4","5","6","7"))
```


```{r}
DefaultAssay(merged5) <- 'RNA'
merged5 <- SCTransform(merged5, vars.to.regress = c("propmt", "nCount_RNA"), verbose = TRUE)
merged5 <- RunPCA(merged5, features = VariableFeatures(object = merged5), npcs=100, verbose=TRUE)
```

```{r}
ElbowPlot(merged5, ndims = 50)
```

```{r}
merged5 <- RunUMAP(merged5, reduction = "pca", dims = 1:40)
merged5 <- FindNeighbors(merged5, reduction = "pca", dims = 1:40)
merged5 <- FindClusters(merged5, graph.name = "SCT_snn", algorithm = 3, resolution = c(0.4), verbose = FALSE)
```

```{r}
DimPlot(merged5, reduction = "umap", label = TRUE, group.by = "SCT_snn_res.0.4")
```

```{r}
DefaultAssay(merged5) <- 'SCT'
rna.markers <- FindAllMarkers(merged5, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.25)
write.csv(rna.markers, file ="./merged5_DGE_GEX_res0.4.csv", quote = FALSE)
```



```{r}
#unmapped object
saveRDS(merged5, "./WT_HIF1AKO_unmapped.rds")
merged5 <- readRDS("./WT_HIF1AKO_unmapped.rds")
DimPlot(merged5)
```


# Reference Mapping
```{r}
andrew_mouse <- readRDS("./MonoTrack_Jan2023_UMAPmodel.rds")
DimPlot(andrew_mouse, reduction = "umap", label = TRUE)
```

```{r}
andrew_mouse <- FindNeighbors(andrew_mouse, reduction = "pca", dims = 1:40)
DimPlot(andrew_mouse, reduction = "umap", label = TRUE)
```


```{r}
andrew_mouse <- RunSPCA(andrew_mouse, assay = 'SCT', graph = 'SCT_snn')
DimPlot(andrew_mouse, reduction = "umap", label = TRUE)
```


```{r}
anchors <- FindTransferAnchors(
  reference = andrew_mouse,
  query = merged5,
  normalization.method = "SCT",
  reference.reduction = "spca",
  reference.assay = "SCT",
  dims = 1:40
)
```

```{r}
merged5 <- MapQuery(
  anchorset = anchors,
  query = merged5,
  reference = andrew_mouse,
  refdata = list(
    celltype = "Names"
  ),
  reference.reduction = "spca",
  reduction.model = "umap"
)
```

```{r}
DimPlot(merged5, reduction = "ref.umap", group.by = "predicted.celltype")
```


```{r}
#mapped object
saveRDS(merged5, "./WT_HIF1AKO_mapped.rds")
myeloid <- readRDS("./WT_HIF1AKO_mapped.rds")
DimPlot(myeloid, reduction = "ref.umap", group.by = "predicted.celltype")
```


```{r}
#do palantir script now
Idents(myeloid) <- "predicted.celltype"
```

#plot of reference dataset
```{r}
levels(x = andrew_mouse) <- c("Trem2", "Gdf15", "MHCII", "IFN", "Prolif", "Arg1", "cDC2", "Mono", "Ccl8", "Res")

png(filename="./andrew reference.png", width=25, height=20, units="cm", res=600)
DimPlot(andrew_mouse, reduction = "umap", label = FALSE, pt.size = 2) + coord_fixed() +
  theme(legend.text=element_text(size=25))+
  scale_color_manual(values = c("#920000","#004949","#009292","#ff6db6","#490092","#006ddb","#24ff24","#db6d00","#b66dff","#6db6ff","#ffff6d","#ffb6db","#b6dbff","#924900"))
dev.off()


```

#plot of mapped data
```{r}
myeloid$predicted.celltype <- factor(x = myeloid$predicted.celltype, levels = c("Trem2", "Gdf15", "MHCII", "IFN", "Prolif", "Arg1", "cDC2", "Mono", "Ccl8", "Res"))

png(filename="./mapped data.png", width=25, height=20, units="cm", res=600)
DimPlot(myeloid, reduction = "ref.umap", label = FALSE, group.by = "predicted.celltype", pt.size = 2) + coord_fixed() +
  theme(legend.text=element_text(size=25))+
  scale_color_manual(values = c("#920000","#004949","#009292","#ff6db6","#490092","#006ddb","#24ff24","#db6d00","#b66dff","#6db6ff","#ffff6d","#ffb6db","#b6dbff","#924900"))
dev.off()

myeloid$condition <- factor(x = myeloid$condition, levels = c("WT", "KO"))

png(filename="./mapped data split.png", width=40, height=20, units="cm", res=600)
DimPlot(myeloid, reduction = "ref.umap", label = FALSE, group.by = "predicted.celltype", pt.size = 2, split.by = "condition") + coord_fixed() +
  theme(legend.text=element_text(size=25))+
  scale_color_manual(values = c("#920000","#004949","#009292","#ff6db6","#490092","#006ddb","#24ff24","#db6d00","#b66dff","#6db6ff","#ffff6d","#ffb6db","#b6dbff","#924900"))
dev.off()
```

#stacked barplot of cell 
```{r}
png(filename="./stacked barplot.png", width=40, height=20, units="cm", res=600)
ggplot(myeloid@meta.data, aes(x = condition, fill = predicted.celltype)) +
  geom_bar(position = "fill", width = 0.95) +
  xlab("Sample") +
  ylab("Proportion") +
  theme(legend.title = element_blank())+ coord_fixed(ratio=5)  +
  theme(legend.text=element_text(size=25)) +
  scale_fill_manual(values = c("#920000","#004949","#009292","#ff6db6","#490092","#006ddb","#24ff24","#db6d00","#b66dff","#6db6ff","#ffff6d","#ffb6db","#b6dbff","#924900"))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(legend.text=element_text(size=25))+ 
  theme(axis.text = element_text(size = 25))
dev.off()
```

#plot of mapping scores

```{r}
DefaultAssay(myeloid) <- "prediction.score.celltype"

png(filename="./mapping score Ccl8.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Ccl8", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score MHCII.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "MHCII", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Trem2.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Trem2", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Gdf15.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Gdf15", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Res.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Res", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Arg1.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Arg1", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Prolif.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Prolif", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score Mono.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Mono", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score IFN.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "IFN", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

png(filename="./mapping score cDC2.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "cDC2", pt.size = 2, reduction = "ref.umap")  + coord_fixed()
dev.off()

```


```{r}
Idents(myeloid) <- "predicted.celltype"
myeloid.averageexpression <- AverageExpression(myeloid, features = c("Ccl8","MHCII","Trem2","Gdf15","Res","Arg1","Prolif","Mono","IFN","cDC2"),
                                               assays = "prediction.score.celltype")
myeloid.averageexpression <- as.matrix(myeloid.averageexpression)
mapping_scores <- myeloid.averageexpression[[1]]
list <- c("Ccl8","MHCII","Trem2","Gdf15","Res","Arg1","Prolif","Mono","IFN","cDC2")

png(filename="./mapping scores heatmap.png", width = 40, height = 20, units ="cm", res =300)
pheatmap(mapping_scores[,list], color=colorRampPalette(c("navy", "white", "orange"))(50), scale="none", cellheight = 30, cellwidth = 30, cexCol=0.5, cluster_rows=FALSE, fontsize_row=25, fontsize_col=25, cluster_cols = FALSE, legend = TRUE, fontsize = 20)
dev.off()
```



```{r}
Idents(myeloid) <- "predicted.celltype"
DefaultAssay(myeloid) <- 'SCT'
rna.markers <- FindAllMarkers(myeloid, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.25)
write.csv(rna.markers, file ="./DGE_GEX_predicted.celltype.csv", quote = FALSE)
```

#heat map of top10 gene from each population for mapped data
```{r}
# top 10 log fc 
#Trem2: Gpnmb, Fabp5, Ctsd, Spp1, Hmox1, Ctsb, Ctsl, Cd63, Prdx1, Syngr1
#Gdf15: Gdf15, Cxcl2, Ccrl2, Ccl4, Tnf, Nfkbia, Cxcl1, Gadd45b, Cd83, Junb
#MHCII: Cd74, H2-Eb1, H2-Aa, H2-Ab1, H2-DMb1, Ccr2, H2-DMa, Plbd1, Tmem176b, Tmem176a
#IFN: Ifit3, Isg15, Ifit2, Rsad2, Irf7, I830012O16Rik, Ms4a4c, Ly6a, Cxcl10, Ifit1
#Prolif: Hist1h2ap, Birc5, Hmgb2, Stmn1, Top2a, Ube2c, 2810417H13Rik, Hist1h2ae, Mki67, Cenpa
#Arg1: Fn1, Arg1, Crip1, AA467197, S100a6, S100a4, S100a10, Cxcl3, Ccl9, Tppp3
#cDC2: Cd209a, H2-Eb1, H2-Aa, H2-Ab1, Cd74, Napsa, Ifitm1, Klrd1, H2-DMb2, Ccl5
#Mono: Plac8, Ly6c2, Chil3, Thbs1, Hp, Gm9733, Ifitm6, Clec4e, Il1b, Plaur
#Ccl8: Ccl8, Sepp1, Wfdc17, Serpinb6a, Folr2, Cbr2, Ctsd, Gas6, Apoe, Npl
#Res: Ccl12, Cbr2, Ccl7, F13a1, Folr2, Hpgd, Mrc1, Ltc4s, C4b, Pf4

top10logfc <- c('Gpnmb', 'Fabp5', 'Ctsd', 'Spp1', 'Hmox1', 'Ctsb', 'Ctsl', 'Cd63', 'Prdx1', 'Syngr1', 'Gdf15', 'Cxcl2', 'Ccrl2', 'Ccl4', 'Tnf', 'Nfkbia', 'Cxcl1', 'Gadd45b', 'Cd83', 'Junb', 'Cd74', 'H2-Eb1', 'H2-Aa', 'H2-Ab1', 'H2-DMb1', 'Ccr2', 'H2-DMa', 'Plbd1', 'Tmem176b', 'Tmem176a', 'Ifit3', 'Isg15', 'Ifit2', 'Rsad2', 'Irf7', 'I830012O16Rik', 'Ms4a4c', 'Ly6a', 'Cxcl10', 'Ifit1', 'Hist1h2ap', 'Birc5', 'Hmgb2', 'Stmn1', 'Top2a', 'Ube2c', '2810417H13Rik', 'Hist1h2ae', 'Mki67', 'Cenpa', 'Fn1', 'Arg1', 'Crip1', 'AA467197', 'S100a6', 'S100a4', 'S100a10', 'Cxcl3', 'Ccl9', 'Tppp3', 'Cd209a', 'H2-Eb1', 'H2-Aa', 'H2-Ab1', 'Cd74', 'Napsa', 'Ifitm1', 'Klrd1', 'H2-DMb2', 'Ccl5', 'Plac8', 'Ly6c2', 'Chil3', 'Thbs1', 'Hp', 'Gm9733', 'Ifitm6', 'Clec4e', 'Il1b', 'Plaur', 'Ccl8', 'Sepp1', 'Wfdc17', 'Serpinb6a', 'Folr2', 'Cbr2', 'Ctsd', 'Gas6', 'Apoe', 'Npl', 'Ccl12', 'Cbr2', 'Ccl7', 'F13a1', 'Folr2', 'Hpgd', 'Mrc1', 'Ltc4s', 'C4b', 'Pf4')

list = c('Trem2', 'Gdf15', 'MHCII', 'IFN', 'Prolif', 'Arg1', 'cDC2', 'Mono', 'Ccl8', 'Res')

myeloid@active.ident <- factor(x = myeloid@active.ident, levels = list)

png(filename="./top10 log fc heatmap.png", width=40, height=40, units="cm", res=300)
DoHeatmap(myeloid, features = top10logfc, group.by = "ident") + scale_fill_viridis(option=  "plasma")
dev.off()
```

#umap of andrew z scores on mapped data
```{r}
#Ccl8

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zCcl8 <- c("Ccl8","Gas6","Fabp5")
pops<-list(zCcl8)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Ccl8_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Ccl8_z")

png(filename="./andrew z score Ccl8.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Ccl8_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#MHCII

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zMHCII <- c("H2-Eb1", "H2-Aa", "Cd74", "H2-Ab1")
pops<-list(zMHCII)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$MHCII_z<-z_scores[1,]

DotPlot(object = myeloid, features = "MHCII_z")

png(filename="./andrew z score MHCII.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "MHCII_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Trem2

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zTrem2 <- c("Trem2", "Fabp5", "Ctsd", "Gpnmb")
pops<-list(zTrem2)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Trem2_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Trem2_z")

png(filename="./andrew z score Trem2.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Trem2_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Gdf15

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zGdf15 <- c("Gdf15", "Tnf", "Ccl4")
pops<-list(zGdf15)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Gdf15_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Gdf15_z")

png(filename="./andrew z score Gdf15.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Gdf15_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Res

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zRes <- c("Lyve1", "Folr2", "Cd163", "Cbr2")
pops<-list(zRes)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Res_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Res_z")

png(filename="./andrew z score Res.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Res_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Arg1

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zArg1 <- c("Arg1", "Fn1", "Cxcl1", "Tppp3")
pops<-list(zArg1)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Arg1_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Arg1_z")

png(filename="./andrew z score Arg1.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Arg1_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Prolif

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zProlif <- c("Mki67", "Top2a", "Stmn1")
pops<-list(zProlif)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Prolif_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Prolif_z")

png(filename="./andrew z score Prolif.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Prolif_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#Mono

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zMono <- c("Plac8", "Ly6c2")
pops<-list(zMono)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$Mono_z<-z_scores[1,]

DotPlot(object = myeloid, features = "Mono_z")

png(filename="./andrew z score Mono.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "Mono_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#IFN

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zIFN <- c("Isg15", "Ifit3", "Irf7", "Cxcl10")
pops<-list(zIFN)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$IFN_z<-z_scores[1,]

DotPlot(object = myeloid, features = "IFN_z")

png(filename="./andrew z score IFN.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "IFN_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

#cDC2

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
zcDC2 <- c("Ifitm1", "Cd209a")
pops<-list(zcDC2)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$cDC2_z<-z_scores[1,]

DotPlot(object = myeloid, features = "cDC2_z")

png(filename="./andrew z score cDC2.png", width=20, height=20, units="cm", res=300)
FeaturePlot(myeloid, features = "cDC2_z", pt.size = 2, reduction = "ref.umap")  + coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()
```

#umap arg1 z score split by wt and ko

```{r}

png(filename="./split z score Arg1.png", width=40, height=20, units="cm", res=600)
FeaturePlot(myeloid, features = "Arg1_z", pt.size = 3, reduction = "ref.umap", split.by = "condition") +
  theme(legend.text=element_text(size=25))+
  theme(legend.position ='right')+
coord_fixed() & scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()
```

#dot plot of z scores across predicted populations
```{r}
#dot plot idents set to condition
Idents(myeloid) <- myeloid$predicted.celltype
list <- c("Trem2","Gdf15","MHCII","IFN","Prolif","Arg1","cDC2","Mono","Ccl8","Res")
myeloid@active.ident <- factor(x = myeloid@active.ident, levels = list)

png(filename = "./z score dot plot across populations.png", width = 25, height = 20, units = "cm", res = 600)
DotPlot(object = myeloid, features = c("Trem2_z", "Gdf15_z", "MHCII_z", "IFN_z", "Prolif_z", "Arg1_z", "cDC2_z", "Mono_z", "Ccl8_z", "Res_z"))+
  coord_fixed(ratio = 1)
dev.off()

```


#differential gene expression between WT and KO

```{r}
library(DESeq2)

myeloid <- SetIdent(myeloid, value = myeloid@meta.data$condition)

WTvKO <- FindMarkers(myeloid, ident.1 = "WT", ident.2 = "KO", test.use = "DESeq2")

wtvsko <- subset(WTvKO, WTvKO$p_val_adj < 0.05)

wtvsko <- subset(wtvsko, wtvsko$avg_log2FC > 0.1 | wtvsko$avg_log2FC < -0.1)

write.csv(wtvsko,"./deseq2 wt v ko.csv", row.names = TRUE)
```

```{r}
#z score of top 30 genes upregulated in KO

DefaultAssay(myeloid) <- "SCT"
expdata <- GetAssayData(myeloid)
ztop30 <- c('Spp1','Fn1','Xist','S100a6','S100a4','Cd9','Il1rn','Ccl9','Ccl6','Crip1','Anxa1','Clec4e','Lgals3','Plin2','Capg','S100a10','Ctsl','Thbs1','Cstb','Anxa2','S100a11','Txn1','Acp5','Arg1','Chil3','Prdx1','Gpnmb','Plp2','Fabp5','Vim')

pops<-list(ztop30)
#Z-Scores
z_scores<-NULL

for (i in 1:length(pops)) {
genes <- pops[[i]]
zz <- which(tolower(rownames(expdata)) %in% tolower(genes))
av <- numeric(ncol(expdata))

geneExp <- as.matrix(expdata[zz, ])
geneExp <- t(scale(t(geneExp)))
geneExp[is.nan(geneExp)] <- 0
z_scores <- rbind(z_scores,(av + colSums(geneExp) / length(zz)))
}
myeloid@meta.data$top30_z<-z_scores[1,]



png(filename="./top 30 ko DE genes z score.png", width=20, height=20, units="cm", res=600)
FeaturePlot(myeloid, features = "top30_z", pt.size = 3, reduction = "ref.umap")  +
  theme(legend.text=element_text(size=25))+
  theme(legend.position ='right')+
  coord_fixed() + scale_color_gradientn(colors=c("#0D0887FF", "#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF"))
dev.off()

```

#differential gene expression between arg1 and all other subpopulations
```{r}
DefaultAssay(myeloid) <- 'SCT'
myeloid <- SetIdent(myeloid, value = myeloid@meta.data$predicted.celltype)
rna.markers <- FindAllMarkers(myeloid, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.1)
write.csv(rna.markers, file ="./DGE_GEX_res0.4.csv", quote = FALSE)

#wikipathways from enrichr website p val < 0.05 log fc > 0.1
rna.markers <- subset(rna.markers, rna.markers$p_val_adj < 0.05)
rna.markers <- subset(rna.markers, rna.markers$avg_log2FC > 0.1)
write.csv(rna.markers, file ="./DGE_GEX_res0.4.csv", quote = FALSE)

#export entries to table from enrichr
p5 <- read.delim2("WikiPathways_2019_Mouse_table pop5.txt")

p5['condition']='p5'
p5['Adjusted.P.value'] <-as.numeric(p5$Adjusted.P.value)
p5['Combined.Score'] <-as.numeric(p5$Combined.Score)
p5 <- arrange(p5,desc(Combined.Score))

p5<-head(p5, 10)

p5['Overlap']<-sapply(p5$Overlap, function(x) eval(parse(text=x)))
p5['Adjusted.P.value'] <-as.numeric(p5$Adjusted.P.value)

terms <- p5$Term

p5['terms']=terms


png(filename="./wikipathways arg1 pop5 mouse.png", width=15, height=15, units="cm", res=600)
ggplot(p5)+ geom_point(aes(x=Combined.Score,y=terms,color=Adjusted.P.value, size=Overlap))+
  scale_color_gradientn(colors=c("red","lightgrey", "blue"), oob=scales::squish)  + 
  scale_y_discrete(limits = rev(p5$terms), labels = function(y) str_wrap(y, width = 35))+
  theme_bw()+
  theme(aspect.ratio = 2)
dev.off()
```

#transcription factor analysis in Arg1 macrophages
```{r}
#P< 0.05 and log2FC>0.1. P value chea2016 dataset in enrichr
t5 <- read.delim2("ChEA_2016_table p5.txt")

t5['Adjusted.P.value'] <-as.numeric(t5$Adjusted.P.value)
t5['Combined.Score'] <-as.numeric(t5$Combined.Score)

t5 <- arrange(t5,desc(Combined.Score))

t5top10<-head(t5, 10)

t5top10['Overlap']<-sapply(t5top10$Overlap, function(x) eval(parse(text=x)))
t5top10['Adjusted.P.value'] <-as.numeric(t5top10$Adjusted.P.value)

terms <- t5top10$Term

t5top10['terms']=terms


png(filename="./chea2016 arg1.png", width=15, height=15, units="cm", res=600)
ggplot(t5top10)+ geom_point(aes(x=Combined.Score,y=terms,color=Adjusted.P.value, size=Overlap))+
  scale_color_gradientn(colors=c("red","lightgrey", "blue"), oob=scales::squish)  + 
  scale_y_discrete(limits = rev(t5top10$terms), labels = function(y) str_wrap(y, width = 35))+
  theme_bw()+
  theme(aspect.ratio = 2)
dev.off()

```

