```{r}
library(CellChat)
library(patchwork)
library(reticulate)
options(stringsAsFactors = FALSE)
#conda create --name clonebase --clone base
#use_condaenv(condaenv = 'clonebase', conda = "C:/Users/fkady/anaconda3/Scripts/conda.exe")
use_condaenv(condaenv = 'clonebase', conda = "C:/Users/Kadyrov/anaconda3/Scripts/conda.exe")

library(Seurat)
library(NMF)
library(ggalluvial)
library(ComplexHeatmap)
```

```{r}
setwd("E:/andrew reclustered no ccrl2 121422/cellchat/comparison")
```

```{r}
cellchat.wt <- readRDS("E:/andrew reclustered no ccrl2 121422/cellchat/cellchat_wt.rds")
cellchat.ko <- readRDS("E:/andrew reclustered no ccrl2 121422/cellchat/cellchat_ko.rds")
```

```{r}
object.list <- list(wt = cellchat.wt, ko = cellchat.ko)
cellchat <- mergeCellChat(object.list, add.names = names(object.list))
cellchat
```

```{r}
save(object.list, file = "cellchat_object.list_wt_ko.RData")
save(cellchat, file = "cellchat_merged_wt_ko.RData")
```

```{r}
gg1 <- compareInteractions(cellchat, show.legend = F, group = c(1,2))
gg2 <- compareInteractions(cellchat, show.legend = F, group = c(1,2), measure = "weight")

png(filename="./compare interactions and interaction strength.png", width=15, height=15, units="cm", res=300)
gg1 + gg2
dev.off()
```

#The differential number of interactions or interaction strength in the cell-cell communication network between two datasets can be visualized using circle plot, where red colored edges represent increased signaling in the second dataset compared to the first one.
```{r}
par(mfrow = c(1,2), xpd=TRUE)

png(filename="./differential interactions circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_diffInteraction(cellchat, weight.scale = T)
dev.off()

png(filename="./differential interaction strength circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_diffInteraction(cellchat, weight.scale = T, measure = "weight")
dev.off()
```

#heatmap differential interactions and interaction strength
```{r}
gg1 <- netVisual_heatmap(cellchat, color.heatmap = c('#2166ac','#b2182b'))
#> Do heatmap based on a merged object
gg2 <- netVisual_heatmap(cellchat, measure = "weight", color.heatmap = c('#2166ac','#b2182b'))
#> Do heatmap based on a merged object

png(filename="./differential interactions strengths heatmap.png", width=40, height=20, units="cm", res=300)
gg1 + gg2
dev.off()
```

```{r}
weight.max <- getMaxWeight(object.list, attribute = c("idents","count"))
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_circle(object.list[[i]]@net$count, weight.scale = T, label.edge= F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(object.list)[i]))
}
```


```{r}
group.cellType <- c(rep('Res'), rep('Mono'), rep('Arg1'))
group.cellType <- factor(group.cellType, levels = c("Res", "Mono", "Arg1"))
object.list <- lapply(object.list, function(x) {mergeInteractions(x, group.cellType)})
cellchat <- mergeCellChat(object.list, add.names = names(object.list))
#> Merge the following slots: 'data.signaling','images','net', 'netP','meta', 'idents', 'var.features' , 'DB', and 'LR'.
```

```{r}
png(filename="./number interactions res mono arg1.png", width=40, height=20, units="cm", res=300)
weight.max <- getMaxWeight(object.list, slot.name = c("idents", "net", "net"), attribute = c("idents","count", "count.merged"))
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_circle(object.list[[i]]@net$count.merged, weight.scale = T, label.edge= T, edge.weight.max = weight.max[3], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(object.list)[i]))
}
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)

png(filename="./differential interactions res mono arg1.png", width=20, height=20, units="cm", res=300)
netVisual_diffInteraction(cellchat, weight.scale = T, measure = "count.merged", label.edge = T)
dev.off()

png(filename="./differential interaction strength res mono arg1.png", width=20, height=20, units="cm", res=300)
netVisual_diffInteraction(cellchat, weight.scale = T, measure = "weight.merged", label.edge = T)
dev.off()
```

```{r}
png(filename="./compare sources and targets.png", width=40, height=20, units="cm", res=300)
num.link <- sapply(object.list, function(x) {rowSums(x@net$count) + colSums(x@net$count)-diag(x@net$count)})
weight.MinMax <- c(min(num.link), max(num.link)) # control the dot size in the different datasets
gg <- list()
for (i in 1:length(object.list)) {
  gg[[i]] <- netAnalysis_signalingRole_scatter(object.list[[i]], title = names(object.list)[i], weight.MinMax = weight.MinMax)
}
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
patchwork::wrap_plots(plots = gg)
dev.off()
```

```{r}
png(filename="./signaling changes res arg1 mono.png", width=75, height=20, units="cm", res=300)
gg1 <- netAnalysis_signalingChanges_scatter(cellchat, idents.use = "Res")
gg2 <- netAnalysis_signalingChanges_scatter(cellchat, idents.use = "Arg1")
gg3 <- netAnalysis_signalingChanges_scatter(cellchat, idents.use = "Mono")
patchwork::wrap_plots(plots = list(gg1,gg2,gg3))
dev.off()
```

```{r}
cellchat <- computeNetSimilarityPairwise(cellchat, type = "functional")
cellchat <- netEmbedding(cellchat, type = "functional")
cellchat <- netClustering(cellchat, type = "functional")
netVisual_embeddingPairwise(cellchat, type = "functional", label.size = 3.5)
```

```{r}
cellchat <- computeNetSimilarityPairwise(cellchat, type = "structural")
cellchat <- netEmbedding(cellchat, type = "structural")
cellchat <- netClustering(cellchat, type = "structural")
# Visualization in 2D-space
netVisual_embeddingPairwise(cellchat, type = "structural", label.size = 3.5)
netVisual_embeddingPairwiseZoomIn(cellchat, type = "structural", nCol = 2)
```

```{r}
rankSimilarity(cellchat, type = "functional")
```

```{r}
gg1 <- rankNet(cellchat, mode = "comparison", stacked = T, do.stat = TRUE)
gg2 <- rankNet(cellchat, mode = "comparison", stacked = F, do.stat = TRUE)

png(filename="./information flow.png", width=40, height=20, units="cm", res=300)
gg1 + gg2
dev.off()
```

```{r}
i = 1
# combining all the identified signaling pathways from different datasets 
pathway.union <- union(object.list[[i]]@netP$pathways, object.list[[i+1]]@netP$pathways)
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 10)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 10)

png(filename="./outgoing signaling.png", width=40, height=20, units="cm", res=300)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
i = 1
# combining all the identified signaling pathways from different datasets 
pathway.union <- union(object.list[[i]]@netP$pathways, object.list[[i+1]]@netP$pathways)
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 10)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 10)

png(filename="./incoming signaling.png", width=40, height=20, units="cm", res=300)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
png(filename="./DiffProb ligand receptor pairs.png", width=10, height=20, units="cm", res=300)
netVisual_bubble(cellchat, sources.use = "Res", targets.use = c("Arg1", "Mono"),  comparison = c(1, 2), angle.x = 45)
dev.off()
```

```{r}
gg1 <- netVisual_bubble(cellchat, sources.use = "Res", targets.use = c("Arg1"),  comparison = c(1, 2), max.dataset = 2, title.name = "Increased signaling in KO", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat, sources.use = "Res", targets.use = c("Arg1"),  comparison = c(1, 2), max.dataset = 1, title.name = "Decreased signaling in KO", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object

png(filename="./DiffProb ligand receptor pairs split.png", width=20, height=10, units="cm", res=300)
gg1 + gg2
dev.off()
```

#with mono
```{r}
gg1 <- netVisual_bubble(cellchat, sources.use = "Res", targets.use = c("Arg1", "Mono"),  comparison = c(1, 2), max.dataset = 2, title.name = "Increased signaling in KO", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat, sources.use = "Res", targets.use = c("Arg1", "Mono"),  comparison = c(1, 2), max.dataset = 1, title.name = "Decreased signaling in KO", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object

png(filename="./DiffProb ligand receptor pairs split with mono.png", width=20, height=10, units="cm", res=300)
gg1 + gg2
dev.off()
```

#differential expression analysis
```{r}
# define a positive dataset, i.e., the dataset with positive fold change against the other dataset
pos.dataset = "ko"
# define a char name used for storing the results of differential expression analysis
features.name = paste0(pos.dataset, ".merged")

# perform differential expression analysis 
# Of note, compared to CellChat version < v2, CellChat v2 now performs an ultra-fast Wilcoxon test using the presto package, which gives smaller values of logFC. Thus we here set a smaller value of thresh.fc compared to the original one (thresh.fc = 0.1). Users can also provide a vector and dataframe of customized DEGs by modifying the cellchat@var.features$LS.merged and cellchat@var.features$LS.merged.info. 

cellchat <- identifyOverExpressedGenes(cellchat, group.dataset = "datasets", pos.dataset = pos.dataset, features.name = features.name, only.pos = FALSE, thresh.pc = 0.1, thresh.fc = 0.05,thresh.p = 0.05, group.DE.combined = FALSE) 
#> Use the joint cell labels from the merged CellChat object

# map the results of differential expression analysis onto the inferred cell-cell communications to easily manage/subset the ligand-receptor pairs of interest
net <- netMappingDEG(cellchat, features.name = features.name, variable.all = TRUE)
# extract the ligand-receptor pairs with upregulated ligands in ko
net.up <- subsetCommunication(cellchat, net = net, datasets = "ko",ligand.logFC = 0.05, receptor.logFC = NULL)
# extract the ligand-receptor pairs with upregulated ligands and upregulated receptors in wt, i.e.,downregulated in ko
net.down <- subsetCommunication(cellchat, net = net, datasets = "wt",ligand.logFC = -0.05, receptor.logFC = NULL)
```


```{r}
gene.up <- extractGeneSubsetFromPair(net.up, cellchat)
gene.down <- extractGeneSubsetFromPair(net.down, cellchat)
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.up, sources.use = "Res", targets.use = c("Arg1"), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.down, sources.use = "Res", targets.use = c("Arg1"), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
png(filename="./DEX ligand receptor pairs split.png", width=20, height=10, units="cm", res=300)
gg1 + gg2
dev.off()
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.up, sources.use = "Res", targets.use = c("Arg1", "Mono"), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat, pairLR.use = pairLR.use.down, sources.use = "Res", targets.use = c("Arg1", "Mono"), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
png(filename="./DEX ligand receptor pairs split with mono.png", width=20, height=10, units="cm", res=300)
gg1 + gg2
dev.off()
```

```{r}
library(wordcloud)

# visualize the enriched ligands in the first condition
computeEnrichmentScore(net.down, species = 'mouse', variable.both = TRUE)
```

```{r}
# visualize the enriched ligands in the second condition
computeEnrichmentScore(net.up, species = 'mouse', variable.both = TRUE)
```


```{r}
pathways.show <- c("GAS") 
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
```

```{r}
par(mfrow = c(1, 2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_chord_gene(object.list[[i]], sources.use = "Res", targets.use = c("Arg1", "Mono"), lab.cex = 0.5, title.name = paste0("Signaling from Res - ", names(object.list)[i]))
}
```


```{r}
cellchat@meta$datasets = factor(cellchat@meta$datasets, levels = c("wt", "ko")) # set factor level
plotGeneExpression(cellchat, signaling = c("SPP1"), split.by = "datasets", colors.ggplot = T)
```

```{r}
cellchat@meta$datasets = factor(cellchat@meta$datasets, levels = c("wt", "ko")) # set factor level
plotGeneExpression(cellchat, signaling = c("BST2"), split.by = "datasets", colors.ggplot = T)
```

```{r}
cellchat@meta$datasets = factor(cellchat@meta$datasets, levels = c("wt", "ko")) # set factor level
plotGeneExpression(cellchat, signaling = c("GAS"), split.by = "datasets", colors.ggplot = T)
```

```{r}
cellchat@meta$datasets = factor(cellchat@meta$datasets, levels = c("wt", "ko")) # set factor level
plotGeneExpression(cellchat, signaling = c("CCL"), split.by = "datasets", colors.ggplot = T)
```

```{r}
save(object.list, file = "cellchat_object.list_wt_ko.RData")
save(cellchat, file = "cellchat_merged_wt_ko.RData")
```


```{r}
myeloid <- readRDS("E:/andrew reclustered no ccrl2 121422/WT_HIF1AKO_mapped.rds")
```

```{r}
png(filename="./chord diagram signaling up ko.png", width=30, height=15, units="cm", res=300)
netVisual_chord_gene(object.list[[2]], sources.use = "Res", targets.use = c("Trem2", "Gdf15", "MHCII", "IFN", "Prolif", "Arg1", "cDC2", "Mono", "Ccl8"), slot.name = 'net', net = net.up, lab.cex = 0.8, small.gap = 3.5, title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
dev.off()

png(filename="./chord diagram signaling down ko.png", width=30, height=15, units="cm", res=300)
netVisual_chord_gene(object.list[[1]], sources.use = "Res", targets.use = c("Trem2", "Gdf15", "MHCII", "IFN", "Prolif", "Arg1", "cDC2", "Mono", "Ccl8"), slot.name = 'net', net = net.down, lab.cex = 0.8, small.gap = 3.5, title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> You may try the function `netVisual_chord_cell` for visualizing individual signaling pathway
dev.off()
```












































