```{r}
library(CellChat)
library(patchwork)
library(reticulate)
options(stringsAsFactors = FALSE)
#conda create --name clonebase --clone base
#use_condaenv(condaenv = 'clonebase', conda = "C:/Users/fkady/anaconda3/Scripts/conda.exe")
use_condaenv(condaenv = 'clonebase', conda = "C:/Users/Kadyrov/anaconda3/Scripts/conda.exe")

library(Seurat)
library(NMF)
library(ggalluvial)
```

```{r}
setwd("E:/reshif1 snseq/cellchat")
```

```{r}
merged <- readRDS("E:/reshif1 snseq/cleaned global object/cleaned_annotated.rds")
DimPlot(merged, group.by = "global.type")
```

```{r}
Idents(merged) <- "genotype"

mergedwt <- subset(merged, idents = c('WT'))
mergedko <- subset(merged, idents = c('KO'))
```

```{r}
rm(merged)
gc()
```


```{r}
cellchatko <- createCellChat(mergedko, group.by = "global.type", assay = "SCT")
```

```{r}
CellChatDB <- CellChatDB.mouse
showDatabaseCategory(CellChatDB)
```

```{r}
#dplyr::glimpse(CellChatDB$interaction)
```

```{r}
#CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling", key = "annotation")
CellChatDB.use <- CellChatDB 
```

```{r}
cellchatko@DB <- CellChatDB.use
```

```{r}
cellchatko <- subsetData(cellchatko)
future::plan("multisession", workers = 4)
cellchatko <- identifyOverExpressedGenes(cellchatko)
cellchatko <- identifyOverExpressedInteractions(cellchatko)

```

```{r}
#this is optional, have to set raw.use = FALSE in computeCommunProb()
#cellchat <- projectData(cellchat, PPI.mouse)  
```

```{r}

cellchatko <- computeCommunProb(cellchatko, type = "triMean")
```

```{r}
cellchatko <- filterCommunication(cellchatko, min.cells = 10)
```


```{r}
df.net <- subsetCommunication(cellchatko)
```

```{r}
write.csv(df.net,"cell-cell communications ko.csv")
```

```{r}
cellchatko <- computeCommunProbPathway(cellchatko)
```

```{r}
cellchatko <- aggregateNet(cellchatko)
```

```{r}
groupSize <- as.numeric(table(cellchatko@idents))

par(mfrow = c(1,2), xpd=TRUE)

png(filename="./ko number of interactions circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_circle(cellchatko@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
dev.off()

png(filename="./ko interactions weight strength circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_circle(cellchatko@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")
dev.off()
```

```{r}
png(filename="./ko interactions weight strength by population.png", width=50, height=50, units="cm", res=300)
mat <- cellchatko@net$weight
par(mfrow = c(4,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}
dev.off()
```

```{r}
df.net.res <- subsetCommunication(cellchatko, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'))
```

```{r}
write.csv(df.net.res,"res-source communications ko.csv")
```



```{r}
png(filename="./ko bubble plot resident source.png", width=30, height=30, units="cm", res=300)
netVisual_bubble(cellchatko, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'), remove.isolate = FALSE)
dev.off()
```


```{r}
png(filename="./ko bubble plot resident source spp1 gas bst2.png", width=15, height=15, units="cm", res=300)
netVisual_bubble(cellchatko, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'), signaling = c("SPP1","GAS", "BST2"), remove.isolate = FALSE)
dev.off()
```

#SPP1 Signaling Pathway Network
```{r}
# Compute the network centrality scores
cellchatko <- netAnalysis_computeCentrality(cellchatko, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
```

# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups

#SPP1
```{r}
png(filename="./ko signaling roles spp1.png", width=15, height=15, units="cm", res=300)
netAnalysis_signalingRole_network(cellchatko, signaling = "SPP1", width = 8, height = 2.5, font.size = 10)
dev.off()
```

#GAS
```{r}
png(filename="./ko signaling roles gas.png", width=15, height=15, units="cm", res=300)
netAnalysis_signalingRole_network(cellchatko, signaling = "GAS", width = 8, height = 2.5, font.size = 10)
dev.off()
```






# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
```{r}
ht1 <- netAnalysis_signalingRole_heatmap(cellchatko, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchatko, pattern = "incoming")

png(filename="./ko signaling role analysis.png", width=40, height=40, units="cm", res=300)
ht1 + ht2
dev.off()
```

#identify and visualize outgoing communication pattern of secreting cells
```{r}
png(filename="./ko cophenetic and silhouette outgoing.png", width=40, height=20, units="cm", res=300)
selectK(cellchatko, pattern = "outgoing")
dev.off()

#values drop when patterns greater than 3
```

```{r}
nPatterns = 3
```

```{r}
png(filename="./ko outgoing communication patterns.png", width=40, height=20, units="cm", res=300)
cellchatko <- identifyCommunicationPatterns(cellchatko, pattern = "outgoing", k = nPatterns)
dev.off()
```


```{r}
# river plot
png(filename="./ko outgoing river plot.png", width=40, height=20, units="cm", res=300)
netAnalysis_river(cellchatko, pattern = "outgoing")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(filename="./ko outgoing dot plot.png", width=30, height=20, units="cm", res=300)
netAnalysis_dot(cellchatko, pattern = "outgoing")
dev.off()
```

#identify and visualize incoming communication pattern of secreting cells
```{r}
png(filename="./ko cophenetic and silhouette incoming.png", width=40, height=20, units="cm", res=300)
selectK(cellchatko, pattern = "incoming")
dev.off()

#values drop when patterns greater than 3
```

```{r}
nPatterns = 3
```

```{r}
png(filename="./ko incoming communication patterns.png", width=40, height=20, units="cm", res=300)
cellchatko <- identifyCommunicationPatterns(cellchatko, pattern = "incoming", k = nPatterns)
dev.off()
```

```{r}
# river plot
png(filename="./ko incoming river plot.png", width=40, height=20, units="cm", res=300)
netAnalysis_river(cellchatko, pattern = "incoming")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(filename="./ko incoming dot plot.png", width=30, height=20, units="cm", res=300)
netAnalysis_dot(cellchatko, pattern = "incoming")
dev.off()
```

```{r}
cellchatko <- computeNetSimilarity(cellchatko, type = "functional")
cellchatko <- netEmbedding(cellchatko, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
cellchatko <- netClustering(cellchatko, type = "functional")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchatko, type = "functional", label.size = 3.5)
```

```{r}
cellchatko <- computeNetSimilarity(cellchatko, type = "structural")
cellchatko <- netEmbedding(cellchatko, type = "structural")
#> Manifold learning of the signaling networks for a single dataset
cellchatko <- netClustering(cellchatko, type = "structural")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchatko, type = "structural", label.size = 3.5)
```


```{r}
saveRDS(cellchatko, file = "cellchat_ko.rds")
```



```{r}
cellchatwt <- createCellChat(mergedwt, group.by = "global.type", assay = "SCT")
```

```{r}
CellChatDB <- CellChatDB.mouse
showDatabaseCategory(CellChatDB)
```

```{r}
#dplyr::glimpse(CellChatDB$interaction)
```

```{r}
#CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling", key = "annotation")
CellChatDB.use <- CellChatDB 
```

```{r}
cellchatwt@DB <- CellChatDB.use
```

```{r}
cellchatwt <- subsetData(cellchatwt)
future::plan("multisession", workers = 4)
cellchatwt <- identifyOverExpressedGenes(cellchatwt)
cellchatwt <- identifyOverExpressedInteractions(cellchatwt)

```

```{r}
#this is optional, have to set raw.use = FALSE in computeCommunProb()
#cellchat <- projectData(cellchat, PPI.mouse)  
```

```{r}

cellchatwt <- computeCommunProb(cellchatwt, type = "triMean")
```

```{r}
cellchatwt <- filterCommunication(cellchatwt, min.cells = 10)
```


```{r}
df.net <- subsetCommunication(cellchatwt)
```

```{r}
write.csv(df.net,"cell-cell communications wt.csv")
```

```{r}
cellchatwt <- computeCommunProbPathway(cellchatwt)
```

```{r}
cellchatwt <- aggregateNet(cellchatwt)
```

```{r}
groupSize <- as.numeric(table(cellchatwt@idents))

par(mfrow = c(1,2), xpd=TRUE)

png(filename="./wt number of interactions circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_circle(cellchatwt@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
dev.off()

png(filename="./wt interactions weight strength circle plot.png", width=20, height=20, units="cm", res=300)
netVisual_circle(cellchatwt@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")
dev.off()
```

```{r}
png(filename="./wt interactions weight strength by population.png", width=50, height=20, units="cm", res=300)
mat <- cellchatwt@net$weight
par(mfrow = c(2,5), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}
dev.off()
```

```{r}
df.net.res <- subsetCommunication(cellchatwt, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'))
```

```{r}
write.csv(df.net.res,"res communications wt.csv")
```

#spp1 heatmap
```{r}
#pathways.show <- c("SPP1")

png(filename="./wt SPP1 signaling network heatmap.png", width=20, height=20, units="cm", res=300)
par(mfrow=c(1,1))
netVisual_heatmap(cellchatwt, signaling = "SPP1", color.heatmap = "Reds")
dev.off()
```

```{r}
png(filename="./wt SPP1 net contribution.png", width=10, height=10, units="cm", res=300)
netAnalysis_contribution(cellchatwt, signaling = "SPP1")
dev.off
```

#spp1-cd44 heatmap
```{r}

png(filename="./wt SPP1 CD44 signaling network heatmap.png", width=20, height=20, units="cm", res=300)
par(mfrow=c(1,1))
netVisual_heatmap(cellchatwt, signaling = "SPP1", color.heatmap = "Reds")
dev.off()
```

#GAS heatmap
```{r}
#pathways.show <- c("SPP1")

png(filename="./wt GAS signaling network heatmap.png", width=20, height=20, units="cm", res=300)
par(mfrow=c(1,1))
netVisual_heatmap(cellchatwt, signaling = "GAS", color.heatmap = "Reds")
dev.off()
```

```{r}
png(filename="./wt GAS net contribution.png", width=10, height=10, units="cm", res=300)
netAnalysis_contribution(cellchatwt, signaling = "GAS")
dev.off
```



```{r}
png(filename="./wt bubble plot resident source.png", width=30, height=30, units="cm", res=300)
netVisual_bubble(cellchatwt, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'), remove.isolate = FALSE)
dev.off()
```


```{r}
png(filename="./wt bubble plot resident source spp1 gas .png", width=15, height=15, units="cm", res=300)
netVisual_bubble(cellchatwt, sources.use = "resident_mac", targets.use = c('myeloid', 'neutrophil', 'fibroblast', 'endocardial', 'endothelial', 'pericyte', 'epicardium', 'nkt', 'cardiomyocyte', 'lymphatic', 'bcell', 'adipocyte', 'smc', 'pdc', 'neuron'), signaling = c("SPP1","GAS"), remove.isolate = FALSE)
dev.off()
```

#SPP1 Signaling Pathway Network
```{r}
# Compute the network centrality scores
cellchatwt <- netAnalysis_computeCentrality(cellchatwt, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
```

# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups

#SPP1
```{r}
png(filename="./wt signaling roles spp1.png", width=15, height=15, units="cm", res=300)
netAnalysis_signalingRole_network(cellchatwt, signaling = "SPP1", width = 8, height = 2.5, font.size = 10)
dev.off()
```

#GAS
```{r}
png(filename="./wt signaling roles gas.png", width=15, height=15, units="cm", res=300)
netAnalysis_signalingRole_network(cellchatwt, signaling = "GAS", width = 8, height = 2.5, font.size = 10)
dev.off()
```




#dominant senders and receivers
```{r}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchatwt)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchatwt, signaling = c("SPP1", "GAS"))
#> Signaling role analysis on the cell-cell communication network from user's input

png(filename="./wt dominant senders and recievers.png", width=40, height=15, units="cm", res=300)
gg1 + gg2
dev.off()
```

# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
```{r}
ht1 <- netAnalysis_signalingRole_heatmap(cellchatwt, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchatwt, pattern = "incoming")

png(filename="./wt signaling role analysis.png", width=40, height=20, units="cm", res=300)
ht1 + ht2
dev.off()
```

#identify and visualize outgoing communication pattern of secreting cells
```{r}
png(filename="./wt cophenetic and silhouette outgoing.png", width=40, height=20, units="cm", res=300)
selectK(cellchatwt, pattern = "outgoing")
dev.off()

#values drop when patterns greater than 3
```

```{r}
nPatterns = 3
```

```{r}
png(filename="./wt outgoing communication patterns.png", width=40, height=20, units="cm", res=300)
cellchatwt <- identifyCommunicationPatterns(cellchatwt, pattern = "outgoing", k = nPatterns)
dev.off()
```


```{r}
# river plot
png(filename="./wt outgoing river plot.png", width=40, height=20, units="cm", res=300)
netAnalysis_river(cellchatwt, pattern = "outgoing")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(filename="./wt outgoing dot plot.png", width=30, height=20, units="cm", res=300)
netAnalysis_dot(cellchatwt, pattern = "outgoing")
dev.off()
```

#identify and visualize incoming communication pattern of secreting cells
```{r}
png(filename="./wt cophenetic and silhouette incoming.png", width=40, height=20, units="cm", res=300)
selectK(cellchatwt, pattern = "incoming")
dev.off()

#values drop when patterns greater than 3
```

```{r}
nPatterns = 3
```

```{r}
png(filename="./wt incoming communication patterns.png", width=40, height=20, units="cm", res=300)
cellchatwt <- identifyCommunicationPatterns(cellchatwt, pattern = "incoming", k = nPatterns)
dev.off()
```

```{r}
# river plot
png(filename="./wt incoming river plot.png", width=40, height=20, units="cm", res=300)
netAnalysis_river(cellchatwt, pattern = "incoming")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(filename="./wt incoming dot plot.png", width=30, height=20, units="cm", res=300)
netAnalysis_dot(cellchatwt, pattern = "incoming")
dev.off()
```

```{r}
cellchatwt <- computeNetSimilarity(cellchatwt, type = "functional")
cellchatwt <- netEmbedding(cellchatwt, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
cellchatwt <- netClustering(cellchatwt, type = "functional")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchatwt, type = "functional", label.size = 3.5)
```

```{r}
cellchatwt <- computeNetSimilarity(cellchatwt, type = "structural")
cellchatwt <- netEmbedding(cellchatwt, type = "structural")
#> Manifold learning of the signaling networks for a single dataset
cellchatwt <- netClustering(cellchatwt, type = "structural")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchatwt, type = "structural", label.size = 3.5)
```


```{r}
saveRDS(cellchatwt, file = "cellchat_wt.rds")
```







































